\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{5pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Gabriel Frigo} \\
  \small +55 11 95570-2000 $|$ \href{mailto:gabriel.frigo4@gmail.com}{gabriel.frigo4@gmail.com} $|$ 
  \href{https://www.linkedin.com/in/gabriel-frigo-b6727b275/}{linkedin.com/in/gabriel-frigo} $|$
  \href{https://github.com/GabrielFrigo4}{github.com/GabrielFrigo4}
\end{center}

\section*{Summary}
Versatile software engineer with solid experience in low-level and high-performance systems programming. Proficient in C, C++, Rust, and Python, with expertise in developing graphics applications (OpenGL, Vulkan, DirectX) and parallel computing (CUDA, OpenCL). Additional skills include developing ML/AI solutions and linear optimization. Seeking a challenging position to architect and implement robust and efficient software solutions.

\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Languages}: C, C++, Rust, C\#, Java, Python, Lua, SQL}
  \resumeItem{\textbf{Libraries \& Frameworks}: CUDA, OpenGL, Vulkan, OpenCV, Pandas, NumPy}
  \resumeItem{\textbf{Tools}: Git, GitHub, Linux, Docker, PostgreSQL, DBeaver, Postman}
  \resumeItem{\textbf{Concepts}: OOP, Data Structures, Algorithms, Linear Optimization, GPGPU}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingList

  \resumeSubheading
    {QI Tech: BaaS Technology}{Jan 2026 -- Mar 2026}
    {Software Engineering Intern}{QI Tech, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developed and maintained RESTful APIs using Python 3 for financial services.}
      \resumeItem{\textbullet\ Designed and structured databases to ensure data integrity and application performance.}
      \resumeItem{\textbullet\ Containerized applications and development environments using Docker.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {Network Flow Problems: Theory, Algorithms and Implementations}{Oct 2025 -- Sep 2026}
    {Network Flow Research}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Combinatorial Optimization}
      \resumeItem{\textbullet\ Graph Theory}
      \resumeItem{\textbullet\ Flow Problem}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {GRUB Competitive Programming}{Jan 2024 -- Present}
    {Team Member}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Competed in the Maratona Paulista de Programação (MPP) and the International Collegiate Programming Contest (ICPC).}
      \resumeItem{\textbullet\ Solved complex algorithmic problems using advanced data structures and C/C++.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {Competitive Robotics Tamandutech}{Jun 2023 -- Present}
    {Software Developer}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developed software and control systems for competitive "mini sumo" robots.}
      \resumeItem{\textbullet\ Applied low-level programming concepts to interface with robotics hardware.}
    \resumeSubHeadingListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList

  \resumeSubheading
    {BioBlocks Extension Project}{Mar 2026 -- Present}
    {Interactive Biochemistry Quiz Game}{Firebase, C\#, Unity}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developing an educational quiz game aimed at helping undergraduate and master's students solidify their foundational knowledge in biochemistry.}
      \resumeItem{\textbullet\ Designed to serve both UFABC students and the external community, with full release scheduled for December 2026.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {OBI Extension Project}{Jan 2026 -- Present}
    {Mentor and Co-creator}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Co-created the initiative in partnership with the coordinating professor to increase the representation and medal count of the Greater ABC region in the Brazilian Informatics Olympiad (OBI).}
      \resumeItem{\textbullet\ Mentored students ranging from 9th grade to university freshmen across multiple difficulty levels (Junior, 1, 2, and Senior) in programming and algorithms.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {SpaceInvaders Game}{Sep 2025 -- Present} 
    {Graphics and GPGPU Project}{C/C++, SDL3, OpenGL, OpenCL, OpenAL}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Built an optimized 2D game using Hardware Acceleration.}
      \resumeItem{\textbullet\ Implemented a GPGPU program to calculate physics.}
      \resumeItem{\textbullet\ Built an extensive and maintainable object architecture.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {BioDefense Project}{Sep 2021 -- Dec 2021}
    {Educational Tower Defense Game}{C\#, Unity}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developed a Tower Defense game designed to educate children and students about the human immune system and disease prevention.}
      \resumeItem{\textbullet\ Implemented gameplay mechanics where players deploy lymphatic system cells to defend against pathogens, utilizing strategic power-ups like antibiotics.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {Point of Sale and Management System}{Jun 2021 -- Jan 2025}
    {Desktop Applications}{Jardim Maquinas, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developed desktop applications including an RTF to PDF converter and webcam image registration.}
      \resumeItem{\textbullet\ Built an NFe (Electronic Invoicing) manager and signer to streamline sales operations.}
    \resumeSubHeadingListEnd

\resumeSubHeadingListEnd

\section{Honors \& Awards}
\resumeSubHeadingList
  \resumeItem{\textbf{Honorable Mention} -- Brazilian Informatics Olympiad (OBI) \hfill \textit{2024}}
  \resumeItem{\textbf{Gold (2022 - 13th National Position), Silver (2018, 2019) and Bronze (2017, 2021) Medals} -- Brazilian Public Schools Math Olympiad (OBMEP)}
  \resumeItem{\textbf{Bronze Medal} -- Paulista Mathematics Olympiad (OPM) \hfill \textit{2021}}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
    {Federal University of ABC, UFABC}{UFABC, SP}
    {B.S. in Science and Technology and Computer Science}{Jun 2023 -- Dec 2027}
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingList
  \resumeItem{\textbullet\ \href{https://efset.org/cert/9uJjv8}{EFSET English Certificate 60/100 (B2 Intermediate)}}
\resumeSubHeadingListEnd

\end{document}
