\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{5pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Gabriel Frigo} \\
  \small +55 11 95570-2000 $|$ \href{mailto:gabriel.frigo4@gmail.com}{gabriel.frigo4@gmail.com} $|$
  \href{https://linkedin.com/in/gabriel-frigo-b6727b275/}{linkedin.com/in/gabriel-frigo} $|$
  \href{https://github.com/GabrielFrigo4}{github.com/GabrielFrigo4} $|$
  \href{https://gabrielfrigo.dev.br}{gabrielfrigo.dev.br}
\end{center}

\section{Summary}
Undergraduate Computer Science student with a versatile profile and solid experience in low-level and high-performance systems programming. Proficient in C, C++, Rust, and Python, with expertise in developing graphics applications (OpenGL, Vulkan, DirectX) and parallel computing (CUDA, OpenCL). Additional skills include the development of ML/AI solutions and linear optimization.

\section{Skills \& Languages}
\resumeSubHeadingList
  \resumeItem{\textbf{Languages}: C, C++, Rust, Zig, Go, C\#, Java, Python, Lua, Assembly, SQL}
  \resumeItem{\textbf{Tools}: Git, GitHub, GitLab, Linux, FreeBSD, Docker, PostgreSQL, DBeaver, Postman}
  \resumeItem{\textbf{Libraries \& Frameworks}: CUDA, OpenGL, Vulkan, OpenCL, SDL3, WinAPI, OpenCV, Pandas, NumPy}
  \resumeItem{\textbf{Concepts}: Data Structures \& Algorithms, Graphs \& Optimization, OOP, Reverse Engineering, GPGPU}
  \resumeItem{\textbf{Soft Skills}: Objective communication; ability to break down complex tasks; goal-oriented; committed to targets and teamwork; fast learner; values small victories.}
  \resumeItem{\textbf{Languages}: Portuguese (Native); English (Intermediate).}
\resumeSubHeadingListEnd

\section{Professional Experience}
\resumeSubHeadingList

  \resumeSubheading
    {QI Tech: BaaS Technology}{Jan/2026 -- Mar/2026}
    {Software Engineering Intern}{QI Tech, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developed and maintained RESTful APIs using Python 3 for financial services.}
      \resumeItem{\textbullet\ Performed database modeling and environment containerization using Docker.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {\href{https://github.com/GabrielFrigo4/IC_Networks_Flow}{Network Flow Problems: Theory and Algorithms}}{Oct/2025 -- Sep/2026}
    {Undergraduate Researcher (CNPq)}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Research focused on Network Flow Algorithms and Combinatorial Optimization.}
      \resumeItem{\textbullet\ Studied Graph Theory and developed algorithmic implementations in C++.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {GRUB Competitive Programming}{Jan/2024 -- Present}
    {Team Member}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Participated in the São Paulo Programming Marathon and the International Collegiate Programming Contest (ICPC).}
      \resumeItem{\textbullet\ Solved complex problems using C/C++ and advanced data structures.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {Green Team Hacker Club (GTHC)}{Dec/2023 -- Present}
    {Project Analyst}{Santo André, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Managed projects and provided technical instruction in the GTHC Low Level / Infrastructure course.}
      \resumeItem{\textbullet\ Taught C/C++, Rust, Zig, and Assembly focused on systems and low-level programming.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {\href{https://github.com/GabrielFrigo4/TT_MiniSumo_Arruela}{Tamandutech Competitive Robotics}}{Jun/2023 -- Present}
    {Software Developer}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developed software and control systems for "mini sumo" category robots.}
      \resumeItem{\textbullet\ Applied low-level programming concepts for hardware integration.}
      \resumeItem{\textbullet\ Additional repository: \href{https://github.com/GabrielFrigo4/TTCC}{TTCC}.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {\href{https://github.com/GabrielFrigo4/PDPD_Ramsey}{PICME Scientific Research}}{Mar/2023 -- Jan/2026}
    {Researcher}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Conducted advanced research in Ramsey Theory and Infinite Combinatorics, focusing on graph substructures and cardinality.}
      \resumeItem{\textbullet\ Developed reports and formal proofs under the PICME excellence program (IMPA/OBMEP).}
    \resumeSubHeadingListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList

  \resumeSubheading
    {\href{https://github.com/GabrielFrigo4/Project_Bioblocks}{BioBlocks Extension Project}}{Mar/2026 -- Present}
    {Interactive Biochemistry Quiz Game}{Firebase, C\#, Unity}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Educational biochemistry game aimed at undergraduate and graduate students.}
      \resumeItem{\textbullet\ Implemented gamified quiz mechanics using Unity and Firebase.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {OBI Extension Project}{Jan/2026 -- Present}
    {Instructor}{UFABC, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Core member of an initiative aimed at increasing regional representation in the Brazilian Informatics Olympiad (OBI).}
      \resumeItem{\textbullet\ Mentored students in algorithms and data structures across multiple competition levels.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {\href{https://github.com/GabrielFrigo4/unix-sock}{Concurrent HTTP Web Server}}{Feb/2026 -- May/2026}
    {Low-Level Systems \& Networking}{C, GNU/BSD Sockets, Caddy, HTTP/2}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developed an HTTP server in C from scratch, operating on the GNU/BSD Sockets API.}
      \resumeItem{\textbullet\ Implemented concurrency based on \textit{forks} (multiprocessing) to handle simultaneous requests.}
      \resumeItem{\textbullet\ Deployed using Caddy reverse proxy for secure termination (HTTPS) and native HTTP/2 support.}
      \resumeItem{\textbullet\ Live Project: \href{https://game.gabrielfrigo.dev.br/}{game.gabrielfrigo.dev.br}}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {SpaceInvaders Game}{Sep/2025 -- Present}
    {Graphics \& GPGPU}{C/C++, SDL3, OpenGL, OpenCL, OpenAL}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Optimized 2D engine with hardware acceleration and an extensible architecture.}
      \resumeItem{\textbullet\ Utilized GPGPU for real-time parallel physics processing.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {\href{https://github.com/GabrielFrigo4/BioDefense}{BioDefense Project}}{Sep/2021 -- Dec/2021}
    {Educational "Tower Defense" Game}{C\#, Unity}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Tower Defense game based on the immune system and disease prevention.}
      \resumeItem{\textbullet\ Developed pathogen defense mechanics using C\# and Unity.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {Point of Sale (POS) \& Management Project}{Jun/2021 -- Jan/2025}
    {Desktop Applications}{Jardim Máquinas, SP}
    \resumeSubHeadingList
      \resumeItem{\textbullet\ Developed an NFe (Electronic Invoicing) manager and an RTF to PDF converter.}
      \resumeItem{\textbullet\ Created a WebCam registration system to optimize commercial workflows.}
    \resumeSubHeadingListEnd

\resumeSubHeadingListEnd

\section{Honors \& Awards}
\resumeSubHeadingList
  \resumeItem{\textbf{Gold (2022 - 13th National Rank), Silver (2018, 2019), and Bronze (2017, 2021) Medals} -- OBMEP (Brazilian Public Schools Math Olympiad)}
  \resumeItem{\textbf{Gold Medals (2019, 2022)} -- OBA (Brazilian Astronomy and Astronautics Olympiad)}
  \resumeItem{\textbf{Silver Medal (2023) and Honorable Mention (2025)} -- CELLM (Logic Competition)}
  \resumeItem{\textbf{Bronze Medal (2021)} -- OPM (São Paulo Mathematics Olympiad)}
  \resumeItem{\textbf{Honorable Mention (2024)} -- OBI (Brazilian Informatics Olympiad)}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
    {Universidade Federal do ABC (UFABC)}{Santo André, SP}
    {B.S. in Science and Technology}{Jun/2023 -- Dec/2027}
  \resumeSubheading
    {Universidade Federal do ABC (UFABC)}{Santo André, SP}
    {B.S. in Computer Science}{Jun/2023 -- Jun/2028}
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingList
  \resumeItem{\textbullet\ \href{https://efset.org/cert/9uJjv8}{EFSET English Certificate 50/100 (B1 Intermediate)}}
\resumeSubHeadingListEnd

\end{document}
